---
title: "P80105_hw1_lc3807"
author: "Linshen Cai"
date: "9.20.2023"
output: github_document
---

I have an R Markdown document now! 


```{r setup, include = FALSE}
library(tidyverse)
```

# Question 1

```{r}
#load all necessary package for Q1
# load dataset
library(moderndive)
library(ggplot2)
data("early_january_weather")
mean_temp = mean(early_january_weather$temp)

```

This dataset show some important information about Newark airpot. The dataset have `r nrow(early_january_weather)` rows and `r ncol(early_january_weather)` colums. The variables in dataset include `r names(early_january_weather)`. The mean temperature in given period is `r mean_temp` F.

```{r}
# Making a scatterplot 
ggplot(data = early_january_weather , aes(y =temp, x = time_hour, color = humid)) + 
  geom_point()
ggsave("scatter_plot.pdf")

```

According to plot, the general trend in temperature is increasing in given time period. 

# Qestion 2

```{r}

# create a random sample of size 10 from a standard Normal distribution
# Create a logical vector indicating whether elements are greater than 0
# Create a character vector of length 10
# Create a factor vector of length 10 with 3 different levels
# creat dateframe

la_df = tibble(
  norm_samp = rnorm(10, mean = 0 , sd = 1),
  vec_logical = norm_samp > 0,
  vec_char = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "g"),
  vec_factor = factor( sample(c("A", "B", "C"), 10, replace = TRUE))
)

la_df

# Try to take mean
mean(pull(la_df,norm_samp))
mean(pull(la_df,vec_logical))
mean(pull(la_df,vec_char))
mean(pull(la_df,vec_factor))

```
When taking mean of each variable, only numeric and logical vector which are norm_samp and vec_logical work. Vector vec_char and vec_factor doesn't work since they are character and factor vector.

```{r, eval = FALSE}

# Convert variables from one type to numeric

vec_logical = as.numeric(pull(la_df,vec_logical))
is.numeric(vec_logical)
vec_char = as.numeric(pull(la_df,vec_char))
is.numeric(vec_char)
vec_factor = as.numeric(pull(la_df,vec_factor))
is.numeric(vec_factor)

```
Using the function as.numeric on a logical vector (LogicalVector), FALSE is converted to 0 and TRUE to 1. This illustrates how logical values are represented numerically in R.

CharacterVector_numeric: Attempts to convert characters to numeric values by applying as.numeric to a character vector (CharacterVector). However, as characters cannot be turned into numbers directly, it yields NA for each character.

FactorVector_numeric: When a factor vector (FactorVector) is applied as.numeric, the factor levels are converted to their underlying integer indices. Depending on the situation, this could not have a valid interpretation for computations like mean.

The arithmetic mean is calculated as predicted by the mean of numeric variables (such as LogicalVector_numeric).
Since characters cannot be meaningfully averaged, attempts to get the mean of a character vector, such as CharacterVector_numeric, return NA.
The numeric form of factor levels (integer indices) is used to calculate the mean of a factor vector, such as FactorVector_numeric, which may not always be useful.









